The Bug Catalog of the Maven Ecosystem

### 2014-02-17 docs/msr.tex
minors
added updated persistence

\maketitle
\begin{abstract}
Examining software ecosystems can provide the research community
with useful information. To examine the ecosystem of
the Maven Central Repository (approximately 265{\sc gb} of data),
we performed an experiment where we statically analyzed the
repository to detect its software bugs. For our analysis we
used FindBugs, a tool that examines Java bytecode to detect
numerous types of bugs. In this paper, we present our data
collection experiment and show how our dataset can be used
to extract interesting findings on software evolution.
\end{abstract}

@@

As we mentioned earlier our data was stored in a
Mongo{\sc db} database, thus all the data were 
converted to the {\sc json} format. Originally, FindBugs output data is in {\sc xml} format. The conversion was a straight forward mapping
of the {\sc xml} elements to {\sc json} objects. In addition, to the FindBugs data, we added a metadata section, which contained
several additional information regarding the jar file that has been processed (Table~\ref{tbl:metadata-description}). The following listing contains an excerpt:

@@

\bibliographystyle{abbrv}
\bibliography{msr}  
\end{document}

>>>>

\maketitle
\begin{abstract}
Examining software ecosystems can provide the research community
with useful information. To examine the ecosystem of
the Maven Central Repository (approximately 265{\sc gb} of data),
we performed an experiment where we statically analyzed the
repository to detect its software bugs. For our analysis we
used FindBugs, a tool that examines Java bytecode to detect
numerous types of bugs. In this paper we present our data collection
experiment and show our findings regarding software evolution.
\end{abstract}

@@

As we mentioned earlier our data was stored in a
Mongo{\sc db} database, thus all the data were 
converted to the {\sc json} format. FindBugs output data is in {\sc xml} format. The conversion was a straight forward mapping
of the {\sc xml} elements to {\sc json} objects. In addition, to the FindBugs data, we added a metadata section, which contained
several additional information regarding the jar file that has been processed (Table~\ref{tbl:metadata-description}). The following listing contains an excerpt:

@@

\bibliographystyle{abbrv}
\bibliography{msr}

\begin{landscape}
  \begin{table}
    \setlength{\extrarowheight}{0.10cm}
    \caption{Bug persistence comparison.}
    \label{tbl:bug_persistence}
    \resizebox{0.95\columnwidth}{!}{
    \input{bug_persistence.tex}}\\
    The matrix presents pairwise Mann-Whitney $U$ test results
    between the different bug categories. Each cell contains the test
    result (the value of $U$), the $p$-value, the average for each
    category and the sample size for each category. Cells in brackets show
    pairs where no statistically significant difference was found.
  \end{table}
\end{landscape}

\end{document}
